Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-10 main.tex
Some modifications

@@

A \bfit{substitution} is a function $\sigma\colon\VAR\to\TERM$ that is
the identity almost everywhere. We denote substitutions as
$\sigma=\sublist{\subst{x_1}{t_1},\ldots,\subst{x_n}{t_n}}$, where
$\sigma(x_i)=t_i$ for $i=1..n$ and $\sigma(x)=x$ for all
$x\notin\set{x_1,\ldots,x_n}$. 
We write $A\sigma$ for the formula
obtained from $A$ by applying $\sigma$, i.e., by simultaneously
replacing all occurrences of $x_i$ by $t_i$.
A \bfit{renaming} is a substitution $\sigma$ with $\sigma(x)\in\VAR$ for all variables.

@@

The \bfit{complement} of a graph $\gG=\tuple{\vG,\eG}$ is
the graph $\compl\gG=\tuple{\vG,\compl\eG}$ where $vw\in\compl\eG$ iff
$vw\neq\eG$.

@@

A \bfit{directed graph} $\gG =\tuple{\vG,\eG}$ is set $V$ of
\bfit{vertices} and a set $\eG\subseteq \vG\times\vG$ of \bfit{direct edges}.
A \bfit{directed graph homomorphism}
$\phi\colon\tuple{\vG,\eG}\to\tuple{\vH,\eH}$ is function $\phi\colon\vG\to\vH$ such that if
$\pair{v,w}\in\eG$ then $\pair{\phi(v),\phi(w)}\in\eH$.

>>>>

\juihsuan{isn't it given by the first four equations? I think that we use the
notation of negation for atoms and formulas. We may also need to precise that each
predicate symbol $p$ has a dual $\dual{p}$.}

@@

A \bfit{substitution} is a function $\sigma\colon\VAR\to\TERM$ that is
the identity almost everywhere. We denote substitutions as
$\sigma=\sublist{\subst{x_1}{t_1},\ldots,\subst{x_n}{t_n}}$, where
$\sigma(x_i)=t_i$ for $i=1..n$ and $\sigma(x)=x$ for all
$x\notin\set{x_1,\ldots,x_n}$. 
We write $A\sigma$ for the formula
obtained from $A$ by applying $\sigma$, i.e., by simultaneously
replacing all occurrences of $x_i$ by $t_i$.
A \bfit{renaming} is a substitution $\sigma$ with $\sigma(x)\in\VAR$ for all variable $x$.

@@

The \bfit{complement} of a graph $\gG=\tuple{\vG,\eG}$ is
the graph $\compl\gG=\tuple{\vG,\compl\eG}$ where $vw\in\compl\eG$ iff
$vw\notin\eG$.

@@

A \bfit{directed graph} $\gG =\tuple{\vG,\eG}$ is a set $\vG$ of
\bfit{vertices} and a set $\eG\subseteq \vG\times\vG$ of \bfit{direct edges}.
A \bfit{directed graph homomorphism}
$\phi\colon\tuple{\vG,\eG}\to\tuple{\vH,\eH}$ is function $\phi\colon\vG\to\vH$ such that if
$\pair{v,w}\in\eG$ then $\pair{\phi(v),\phi(w)}\in\eH$.
